Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
Explain what is presented by the grey scales Fig. 6 a,b: #8
fill in a space between the captions to make it more readable in Fig 2c,d #10

\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

>>>>

\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}\hspace{0.05\linewidth}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2.png}
  \label{fig:building-lod2}
}\hspace{0.05\linewidth}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

@@

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.7\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
}\hspace{0.02\linewidth}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}
